---
title: "16_11"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

```{r echo=TRUE}
library(dplyr)
library(dslabs)
library(tidyverse)
```

1.  ::: {#Q1}
    A famous athlete has an impressive career, winning 70% of her 500
    career matches. However, this athlete gets criticized because in
    important events, such as the Olympics, she has a losing record of 8
    wins and 9 losses. Perform a Chi-square test to determine if this
    losing record can be simply due to chance as opposed to not
    performing well under pressure.
    :::

```{r echo=TRUE}
two_by_two <- data.frame(won=c("win","lose"), 
                         olympic=c(8,9), 
                         other=c(350-8,150-9)) 

chisq_test <- two_by_two %>% select(-won) %>% chisq.test() 

chisq_test$p.value

```

The chance that the null hypothesis is true, that the difference between
overall and Olympic performance is zero, is p: .0671%, low. Possible
that the difference arises from performance under pressure.

2.  ::: {#Q2}
    Why did we use the Chi-square test instead of Fisher's exact test in
    the previous exercise?
    :::

    A.  It actually does not matter, since they give the exact same
        p-value.

    B.  Fisher's exact and the Chi-square are different names for the
        same test.

    C.  Because the sum of the rows and columns of the two-by-two table
        are not fixed so the hypergeometric distribution is not an
        appropriate assumption for the null hypothesis. For this reason,
        Fisher's exact test is rarely applicable with observational
        data.

    D.  Because the Chi-square test runs faster.

    Answer: C

3.  ::: {#Q3}
    Compute the odds ratio of "losing under pressure" along with a
    confidence interval.
    :::

Odds Ratio:

```{r}
odds_ratio=(9/8)/(141/342)
odds_ratio

```

Confidence Interval:

```{r}
log_or <- log(odds_ratio)
se <- two_by_two %>% select(-won) %>% summarize(se = sqrt(sum(sum(1/olympic)+sum(1/other)))) %>% pull(se)
ci <- log_or + c(-1,1) * qnorm(0.975) * se
exp(ci)

```

4.  ::: {Q4}
    Notice that the p-value is larger than 0.05 but the 95% confidence
    interval does not include 1. What explains this?
    :::

```{=html}
<!-- -->
```
A.  We made a mistake in our code.
B.  These are based on t-statistics so the connection between p-value
    and confidence intervals does not apply.
C.  Different approximations are used for the p-value and the confidence
    interval calculation. If we had a larger sample size the match would
    be better.
D.  We should use the Fisher exact test to get confidence intervals.

Answer(C)

5.  ::: {#Q5}
    Multiply the two-by-two table by 2 and see if the p-value and
    confidence retrieval are a better match.
    :::

```{r}
two_by_two <- data.frame(won=c("win","lose"), 
                         olympic=c(2*8,2*9), 
                         other=c(2*342,2*141))
chisq_test <- two_by_two %>% select(-won) %>% chisq.test() 
chisq_test$p.value

```
```{r}
se <- two_by_two %>% select(-won) %>% summarize(se = sqrt(sum(sum(1/olympic)+sum(1/other)))) %>% pull(se)
ci <- log_or + c(-1,1) * qnorm(0.975) * se
exp(ci)

```

